An object deserves more than a single name

### 2018-12-20 papers/ACL2019/acl19_naming.tex
progress in intro

The goal of this paper is to extend some existing, large-scale resources available for language \& vision research in a way that they can serve as a solid and broad empirical basis for investigations into object naming. 
Thus, while large amounts images from different domains paired with verbal descriptions are generally available, none of the existing corpora records more than a few annotations per object.
Even VisualGenome \cite{krishna2016visualgenome}, one of the most exhaustively annotated resources to date, only provides a single, manually annotated object description (including a single name) per object. 
Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g. object labels are typically quite general as in Flickr30k \cite{plummer2015flickr30kentities} (e.g.,~\cat{people, animals, bodyparts, clothing}) or taxonomically heterogeneous as in MS COCO \cite{mscoco} (e.g.,~\cat{people, baseball glove, bird}).
These two shortcomings - few names per object and inconsistent labeling of categories - make it difficult to get reliable and stable predictions as to how speakers will likely name a given object.\sz{need to make this point more clear}

>>>>

The goal of this paper is to extend some existing, large-scale resources available for language \& vision research in a way that they can serve as a solid and broad empirical basis for investigations into object naming. 
Thus, while large amounts images from different domains paired with verbal descriptions are generally available, none of the existing corpora records more than a few annotations per object.
Even VisualGenome \cite{krishna2016visualgenome}, one of the most exhaustively annotated resources to date, only provides a single, manually annotated object description (including a single name) per object. 
Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g. object labels are typically quite general as in Flickr30k \cite{plummer2015flickr30kentities} (e.g.,~\cat{people, animals, bodyparts, clothing}) or taxonomically heterogeneous as in MS COCO \cite{mscoco} (e.g.,~\cat{people, baseball glove, bird}).
These two shortcomings - few names per object and inconsistent labeling of categories - make it difficult to assess (i) how representative nmaing choices are, (ii) how they related to the taxonomic properties of the object  ... get reliable and stable predictions as to how speakers will likely name a given object.\sz{need to make this point more clear}
